Spectroscopic confirmation of very-wide binaries and large-separation comoving stars from \textsl{Gaia DR1}

### 2017-07-07 paper/comoving-followup.tex
add new table to map new group id to old one and get pair of observations
sketch discussion and conclusion

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{genuine_cmd_rave.pdf}
  \end{center}
  \caption{%
    Color-magnitude diagram of \emph{genuine} comoving star pairs plotted over
    the density of all \tgas\ sources within 200 pc; similar to
    \figurename~\ref{fig:sample-cmd}, but for only the genuine comoving
    pairs.
    Several interesting pairs that include main-sequence and giant component
    stars are highlighted in the text
    (\sectionname~\ref{sec:interesting-pairs}).
    \label{fig:genuine-cmd}}
\end{figure}

\todo{Highlight the MS-Giant pairs}
\todo{Highlight the binary sequence-main sequence pairs}

@@

Once chemical homogeneity understood amongst stars of same spectral type, can be used to calibrate stellar models across the HR diagram: should have same age, chemistry, etc. Also tests of chemical enrichment due to planetary systems

@@

\todo{Cross-match with exoplanets catalog http://exoplanets.org/csv-files/exoplanets.csv}

@@

Abundances!

- Stellar rotation of evolved-main sequence
- Full catalog should contain Shaya and Olling, cross-match to RV surveys

@@

>>>>

\todo{Highlight the G subgiant-A pair}
\todo{Highlight a binary sequence-main sequence pair}
\todo{Highlight the largest mag difference MS pair}

@@

% \begin{figure}[htbp]
%   \begin{center}
%     \includegraphics[width=\linewidth]{genuine_cmd_rave.pdf}
%   \end{center}
%   \caption{%
%     Color-magnitude diagram of \emph{genuine} comoving star pairs plotted over
%     the density of all \tgas\ sources within 200 pc; similar to
%     \figurename~\ref{fig:sample-cmd}, but for only the genuine comoving
%     pairs.
%     Several interesting pairs that include main-sequence and giant component
%     stars are highlighted in the text
%     (\sectionname~\ref{sec:interesting-pairs}).
%     \label{fig:genuine-cmd}}
% \end{figure}

@@

Abundance of large-separation pairs

Need precise chemical information

But at very large separations, how do you convince yourself that a pair was truly coeval? Same chemistry? To what precision? What about chemical differences from planet formation?

Going forward, will have to use hierarchical mixture models to study population of singles in conjunction

Great reward: Once chemical homogeneity understood amongst stars of same spectral type, can be used to calibrate stellar models across the HR diagram: should have same age, chemistry, etc. Also tests of chemical enrichment due to planetary systems

@@

@@

Abundances - future work, Coronado in prep.!

Dynamical capture at these radii are improbable, but <insert words about binary-binary encounters from Nathan>

@@

Low-resolution spectroscopic follow-up of comoving pairs.

Using relative RV's, confirm a sample of very wide separation comoving star pairs.

Either wide binaries, unbound binaries, or dissolving clusters

Need much larger sample with no cuts on separation or signal-to-noise to study true separation distribution

Gaia DR2 for G < 12, but really we need a concerted effort to obtain spectroscopy of wide pairs.
